---
title: "Analyze Data"
author: "Sayali Kedar Oak"
output:
  pdf_document: default
  html_notebook: default
---
```{r}
library(RMySQL)
dbcon = dbConnect(RMySQL::MySQL(),host='localhost',port=3306,user='root',
                  password='root123')
```

```{sql connection=dbcon}
USE practicum2DB
```

## Report Title : Popular Journals for a given time period

## Analytical Query I: 

Top five journals with the most articles published in them for the time period. 
Think about how you would best present this information so it is easily usable 
by an analyst or manager.


Consider the time period as 1975 - 1980
The following query gives information about the top 5 journals in which most 
articles were published during this time period. 
The best way to present this information will be in the form of a table like the
one from the output of the query, or a bar graph.

The following report provides information about the most popular journals for
authors. Since it gives information about the journals which published the 
most number of articles for a given time period.


```{sql connection=dbcon}

SELECT JournalTitle, SUM(JournalFacts.NumArticlesPerYear) as TotalArticles
FROM JournalFacts
JOIN JournalDimension ON JournalFacts.JournalID = JournalDimension.JournalID
JOIN TimeDimension ON JournalFacts.TimeID = TimeDimension.TimeID
WHERE TimeDimension.Year BETWEEN 1975 AND 1980 
GROUP BY JournalDimension.JournalTitle
ORDER BY TotalArticles DESC
LIMIT 5;

```

## Report title: Articles published in journals per quarter.

##Analytical Query II: 
Number of articles per journal per year broken down by quarter. 
Again, think of a good way to show this. Is a table better than a visualization 
or is it better to use a visualization.

In this case, a visualization is a better way to present the data provided.
This is because they table may cause confusion since there is a lot of numerical
data present.

The following report gives information about the number of articles published in
journals per quarter. 

```{sql connection=dbcon}
SELECT JournalTitle, TimeDimension.Year, TimeDimension.Quarter, 
SUM(NumArticlesPerQuarter) as TotalArticles
FROM JournalFacts
JOIN JournalDimension ON JournalFacts.JournalID = JournalDimension.JournalID
JOIN TimeDimension ON JournalFacts.TimeID = TimeDimension.TimeID
GROUP BY JournalTitle, TimeDimension.Year, TimeDimension.Quarter
ORDER BY JournalTitle AND TimeDimension.Quarter AND TimeDimension.Year;

```


```{r}
s <- dbDisconnect(dbcon)
```

